03_traitement

### 2019-12-18 r/03_traitement.Rmd
logit ps_car_11_cat

```{r}
res_famd<-readRDS("./../data/res_famd.rds")
```

```{r}
coord<-res_famd$quali.var$coord %>% as.data.frame()
liste_var_factor = type_col[type_col == "factor"]
liste_var_factor<-names(liste_var_factor[-1])
name<-c()

@@

@@

>>>>

```{r}
res_famd<-readRDS("./../data/res_famd.rds")
coord<-res_famd$quali.var$coord %>% as.data.frame()
liste_var_factor = type_col[type_col == "factor"]
liste_var_factor<-names(liste_var_factor[-1])
name<-c()

@@

## Régression logistique sur variable à 104 modalité

```{r}
df <- data_sel %>% filter(dataset=="train")
model<-glm(data = df, target ~ ps_car_11_cat, family = binomial(link = logit))
res<-summary(model)
df<-cbind.data.frame(ps_car_11_cat=gsub("ps_car_11_cat","",rownames(res$coefficients)),res$coefficients)
df<- df %>% select(ps_car_11_cat,Estimate)
df$ps_car_11_cat<-as.factor(df$ps_car_11_cat)
data_sel<- left_join(data_sel,df,"ps_car_11_cat")
data_sel$ps_car_11_cat<-data_sel$Estimate
data_sel <- data_sel %>% select(-Estimate)
ggplot(data_sel, aes(ps_car_11_cat,color=target))  +
  geom_density() +ggtitle("ps_car_11_cat")
```

@@

```{r}
train<-data_sel %>% filter(dataset=="train") %>% select(-dataset)
test<-data_sel %>% filter(dataset=="test") %>% select(-dataset)

type_col = sapply(train, class)

saveRDS(object = type_col,
      file = "./../data/type_col.rds")

write.csv(x = train,
          file = "./../data/train.csv",
          quote = T,
          row.names = F)
write.csv(x = test,
          file = "./../data/test.csv",
          quote = T,
          row.names = F)
```
